---
title: "Internship Report in R"
output: pdf_document
---

## Internship Report   
```{r echo = TRUE}  
rm(list=ls())
```  

## Importing Packages    
```{r echo = FALSE, include=FALSE, warning = FALSE, message = FALSE}  
#Including Packages 


installIfAbsentAndLoad <- function(neededVector) {
  for(thispackage in neededVector) {
    if( ! require(thispackage, character.only = T) )
    { install.packages(thispackage)}
    require(thispackage, character.only = T)
  }
}

needed <- c('purrr')  
installIfAbsentAndLoad(needed) 
```  

## Data Preprocessing Steps  
```{r echo = TRUE}  

###### Read the data in ######
data <- read.csv(file='insurance.csv')

###### Print the first rows ######
print(head(data, 5))

###### Print the columns' names ######
print(colnames(data))

###### Print number of rows ######
print(nrow(data))

###### Converting to Numeric Variables ###### 
sex <- ifelse(data["sex"] == "female", 0, 1)
smoker  <- ifelse(data["smoker"] == "yes", 1, 0)
region <- as.numeric(data$region)

##### Replacing columns in the Data ###### 
data["sex"] <-  sex
data["smoker"] <-  smoker
data["region"] <- region
```  

## Linear Models - using the `purrr` package to get individual models  
```{r echo = TRUE}  
###### Linear Regression ######
vars = c('age', 'sex', 'bmi', 'children', 'smoker', 'region')
#Using the purrr package to run all the models corresponding to the predictors
models <- vars %>% paste ('charges ~', .) %>% map(as.formula) %>% map(lm, data = data)
```  

## Summaries of the Models  

Age  
```{r echo = T}
# age summary
summary(models[[1]])
```  
Sex 

```{r echo = T}
# sex summary
summary(models[[2]])
```  
BMI 

```{r echo = T}
# bmi summary
summary(models[[3]])
```  
Children  

```{r echo = T}
# children summary
summary(models[[4]])
```  
Smoker  

```{r echo = T}
# smoker summary
summary(models[[5]])
```  
Region  

```{r echo = T}
# region summary
summary(models[[6]])
```     
  
******  


## Linear Model with All Predictors     
```{r echo = TRUE} 
###### Model with all the predictors  ###### 
allpreds <- lm(charges ~ ., data = data)
```    

## Summary of the Model     
```{r echo = T}
###### Summary ###### 
summary(allpreds)
```  

******  

## Linear Model with the Most Relevant Predictors  
``` {r echo = T}
most_rel <- lm(charges ~ age + bmi + children + smoker, data = data)
```  





## Summary of the Model  
```{r echo = T}
summary(most_rel)
```


## For Comparison with Python Models (Links)
[GitHub Pages for the Internship](https://arcelioeperez.github.io/dash-app/) | [GitHub Repository](https://github.com/arcelioeperez/dash-app/tree/gh-pages)  
[Heroku App - using Dash and Plotly](https://my-internship-app.herokuapp.com/)  

